---
title: "Map of Electric Fuel Stations"
author: "Rohit Padebettu"
date: "10/21/2016"
output: html_document
---
## Data Source
Alternative Fuel gas station data is downloaded from the following website ( *might need to register* ) [Alternative Fuel Stations](http://www.afdc.energy.gov/data_download)

## Read and Process Data
We begin by loading the raw data into R and then processing it to only include the `ELEC` gas stations with location, address and contact information.

We create the `PopText` column in the dataframe to allow html rendering of the name and contact information.
```{r, eval=TRUE, echo=TRUE,warning=FALSE}
suppressPackageStartupMessages(library(dplyr))
data_raw <- read.csv("./alt_fuel_stations (Oct 21 2016).csv",
                 header = TRUE,sep = ",",stringsAsFactors = FALSE)

data_select<- data_raw%>%
    select(ID,Station.Name,Longitude,Latitude
           ,Street.Address,City,State,ZIP,Station.Phone,
           Fuel.Type.Code)%>%
    filter(Fuel.Type.Code=="ELEC")%>%
    mutate(PopText = paste(sep = "<br />",
                        "<dl>",
                        paste("<dt><b>Name:</b></dt>","<dd>",
                              Station.Name,"</dd>"),
                        paste("<dt><b>Street:</b></dt>","<dd>",
                              Street.Address,"</dd>"),
                        paste("<dt><b>City, State:</b></dt>",
                              "<dd>",City,", ",State,"</dd>"),
                        paste("<dt><b>Zip Code:</b></dt>",
                              "<dd>",ZIP,"</dd>"),
                        paste("<dt><b>Phone:</b></dt>",
                              "<dd>",Station.Phone,"</dd>"),
                        "</dl>"))

```

## Map the Data
We then use the `leaflet` library to map the data from the dataset processed above

```{r, eval=TRUE}
suppressPackageStartupMessages(library(leaflet))
my_map <- leaflet() %>%
    addTiles() %>% 
    addMarkers(lat=data_select$Latitude, lng=data_select$Longitude, 
               popup=data_select$PopText,
               clusterOptions = markerClusterOptions())
my_map
```